Pillar 2 - (STM) Topic Modeling

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
saveing models

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
```

>>>>

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
my_models <-  list(use = stm_model, eval = stm_eval_model)
save(my_models , file="STM_models.RDATA")
```
